A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking

### 2021-09-24 博士/论文提交/adversarial_attack/TCSVT/大修/正文/main.tex
表头写反了
更正GOT-Val大小写

\begin{table}[t]
  \centering
  \caption{Overall attack results on OTB-15, GOT-Val and LaSOT.}
  \begin{tabular}{rrccc}
  \toprule
  \multirow{2}{*}{Benchmarks} & \multirow{2}{*}{Metrics} & Before    & Targeted & Untargeted  \\
                            &                         & Attack & Attack & Attack     \\ 
  \midrule
  \multirow{2}{*}{OTB-15} 
  & AO   & 0.642 & 0.063 & 0.759\\
  & Precision & 0.861 & 0.092 & 0.795\\
  \midrule
  \multirow{2}{*}{GOT-Val} 
  & SR & 0.897 & 0.123 & 0.890\\
  & AO & 0.760 & 0.153 & 0.840 \\
  \midrule
  \multirow{3}{*}{LaSOT} 
  & Precision  & 0.514 & 0.046 & 0.605\\
  & Norm. Prec.& 0.551 & 0.048 & 0.702\\
  & AO         & 0.525 & 0.069 & 0.691\\
  %& Succ. rate  & 0.626 & 0.016 & 0.834\\
  \midrule
  \multicolumn{2}{r}{FPS} & 58 & 58 & 58\\
  \bottomrule
  \end{tabular}
  \label{tab:benchmark results}
\end{table}

@@

%%%%%%%% 消融实验：YCbCr攻击 %%%%%%%%
\begin{table}[t]
  \centering
  \caption{Influence of different ways to perturb the search image. The first row demonstrates the attack performance of the RGB attack method, i.e., the attack method proposed in Section III. The second row demonstrates the attack performance of YCbCr attack method: first we convert the search image into YCbCr color space, then add perturbations over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel. The attack performance is evaluated according to AO/SR on GOT-Val.}
  \label{table:perturb}
  \begin{tabular}{@{}rcccccc@{}}
  \toprule
  \multirow{2}{*}[-1pt]{\begin{tabular}[c]{@{}c@{}}Way to perturb\\ the search image\end{tabular}} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} & \multicolumn{2}{c}{SSIM} \\ \cmidrule{2-7}
                                                         & AO                                      & SR                               & AO                & SR                   & $\delta$          & $p$  \\ \midrule
  RGB Attack                                             & 0.153                                   & 0.123                            & 0.840             & 0.890                & 0.56              & 0.79 \\
  YCbCr Attack                                           & 0.246                                   & 0.227                            & 0.682             & 0.756                & 0.78              & 0.79 \\ \bottomrule        
  \end{tabular}
\end{table}
\uline{\textit{Ablation Study: Attack in YCbCr Space}
The shortcoming of our method is the more conspicuous perturbation values compared to existing target tracking attack algorithms. Other methods add perturbations over the entire search image, whereas we need to add perturbations over a very small region of $64 \times 64$, which increases the learning difficulty and makes the perturbation values large. To reduce perceptibility while achieving the targeted attack, we consider a new way to perturb the search image: first we convert the search image into YCbCr color space, then add the perturbation over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel. Different from RGB color space, YCbCr color space encodes a color image similar to human eyes’ retina, which separates the RGB components into a luminance component (Y) and two chrominance components (Cb as blue projection and Cr as red projection). We choose YCbCr color space since its color channels are less correlated and quite independent than RGB \cite{8630918}. While considering the color sensitivity of human vision system, the CbCr channels are less sensitive than the Y channel \cite{8630918}. This means that the patch added in the CbCr channels has better performance of transparency.
For the template image, we convert it into YCbCr color space, then add the perturbation over the entire template image in all YCbCr channels. The perturbed template and search images are then converted into RGB color space and fed into the tracking network. The other steps of the training process are the same as the attack method in Section III. The experimental result is shown in Table \ref{table:perturb}. As we can see, the performance of attacking the YCbCr color space is slightly degraded compared to attacking the RGB color space. Specifically, in terms of AO on GOT-VAL, the targeted attack performance is 0.680, and the untargeted attack performance is 0.246. However, attacking the YCbCr color space brings better imperceptibility (see Figure \ref{fig:YCbCr}). Compared with attacking the RGB space, the SSIM of $p$ increases from 0.56 to 0.78. The SSIM of $\delta$ remains unchanged at 0.79.
}

>>>>

\begin{table}[t]
  \centering
  \caption{Overall attack results on OTB-15, GOT-Val and LaSOT.}
  \begin{tabular}{rrccc}
  \toprule
  \multirow{2}{*}{Benchmarks} & \multirow{2}{*}{Metrics} & Before    & Untargeted & Targeted  \\
                            &                         & Attack & Attack & Attack     \\ 
  \midrule
  \multirow{2}{*}{OTB-15} 
  & AO   & 0.642 & 0.063 & 0.759\\
  & Precision & 0.861 & 0.092 & 0.795\\
  \midrule
  \multirow{2}{*}{GOT-Val} 
  & SR & 0.897 & 0.123 & 0.890\\
  & AO & 0.760 & 0.153 & 0.840 \\
  \midrule
  \multirow{3}{*}{LaSOT} 
  & Precision  & 0.514 & 0.046 & 0.605\\
  & Norm. Prec.& 0.551 & 0.048 & 0.702\\
  & AO         & 0.525 & 0.069 & 0.691\\
  %& Succ. rate  & 0.626 & 0.016 & 0.834\\
  \midrule
  \multicolumn{2}{r}{FPS} & 58 & 58 & 58\\
  \bottomrule
  \end{tabular}
  \label{tab:benchmark results}
\end{table}

@@

%%%%%%%% 消融实验：YCbCr攻击 %%%%%%%%
\begin{table}[t]
  \centering
  \caption{Influence of different ways to perturb the search image. The first row demonstrates the attack performance of the RGB attack method, i.e., the attack method proposed in Section III. The second row demonstrates the attack performance of YCbCr attack method: first we convert the search image into YCbCr color space, then add perturbations over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel. The attack performance is evaluated according to AO/SR on GOT-Val.}
  \label{table:perturb}
  \begin{tabular}{@{}rcccccc@{}}
  \toprule
  \multirow{2}{*}[-1pt]{\begin{tabular}[c]{@{}c@{}}Way to perturb\\ the search image\end{tabular}} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} & \multicolumn{2}{c}{SSIM} \\ \cmidrule{2-7}
                                                         & AO                                      & SR                               & AO                & SR                   & $\delta$          & $p$  \\ \midrule
  RGB Attack                                             & 0.153                                   & 0.123                            & 0.840             & 0.890                & 0.56              & 0.79 \\
  YCbCr Attack                                           & 0.246                                   & 0.227                            & 0.682             & 0.756                & 0.78              & 0.79 \\ \bottomrule        
  \end{tabular}
\end{table}
\uline{\textit{Ablation Study: Attack in YCbCr Space}
The shortcoming of our method is the more conspicuous perturbation values compared to existing target tracking attack algorithms. Other methods add perturbations over the entire search image, whereas we need to add perturbations over a very small region of $64 \times 64$, which increases the learning difficulty and makes the perturbation values large. To reduce perceptibility while achieving the targeted attack, we consider a new way to perturb the search image: first we convert the search image into YCbCr color space, then add the perturbation over the entire search image in the Y channel, and add perturbations over a very small region of $64 \times 64$ in the CbCr channel. Different from RGB color space, YCbCr color space encodes a color image similar to human eyes’ retina, which separates the RGB components into a luminance component (Y) and two chrominance components (Cb as blue projection and Cr as red projection). We choose YCbCr color space since its color channels are less correlated and quite independent than RGB \cite{8630918}. While considering the color sensitivity of human vision system, the CbCr channels are less sensitive than the Y channel \cite{8630918}. This means that the patch added in the CbCr channels has better performance of transparency.
For the template image, we convert it into YCbCr color space, then add the perturbation over the entire template image in all YCbCr channels. The perturbed template and search images are then converted into RGB color space and fed into the tracking network. The other steps of the training process are the same as the attack method in Section III. The experimental result is shown in Table \ref{table:perturb}. As we can see, the performance of attacking the YCbCr color space is slightly degraded compared to attacking the RGB color space. Specifically, in terms of AO on GOT-Val, the targeted attack performance is 0.680, and the untargeted attack performance is 0.246. However, attacking the YCbCr color space brings better imperceptibility (see Figure \ref{fig:YCbCr}). Compared with attacking the RGB space, the SSIM of $p$ increases from 0.56 to 0.78. The SSIM of $\delta$ remains unchanged at 0.79.
}
